\section{Introduction}
\label{sec:intro}

Two paradigms now dominate robot learning. \emph{Vision-language-action} (VLA)
models predict actions from frozen weights; \emph{code-as-policy} agents instead
write executable programs and improve them from experience~\citep{codeaspolicies,aspire}.
This survey is organized around that fault line.

\paragraph{Why now: the skill stack.}
The app store for robot skills has arrived---Unitree UniStore ships one-tap,
cross-model motion downloads~\citep{unistore2026}. But every skill in it is
\emph{canned playback}: the least-capable point on our map. The skill stack has
three layers---\textbf{(1) Build} (how skills are created, \S\ref{sec:taxonomy}--\S\ref{sec:techniques}),
\textbf{(2) Distribute} (marketplaces and hubs), and \textbf{(3) Adapt} (on-device
self-improvement, \S\ref{sec:code}). UniStore is layer~2 over static layer-1 skills;
the promised value---``adjust grip per fruit so nothing bruises''---lives in layer~3,
which no shipped skill does today.

\paragraph{Contributions.}
(i) a taxonomy of robot-learning techniques organized by \emph{weights vs.\ skills}
(\S\ref{sec:taxonomy}); (ii) a deep-dive arranging code-as-policy by \emph{degree of
self-improvement} and isolating the un-surveyed \S3.1.5 cell (\S\ref{sec:code});
(iii) a companion map of the ``skills'' pole (\S\ref{sec:skill}); and (iv) an
open-problems agenda for the emerging skill economy (\S\ref{sec:open}).

\paragraph{Related surveys.}
Table~\ref{tab:survey_compare} contrasts the topical coverage of the closest surveys with
ours, and Table~\ref{tab:surveys} places them on a timeline. Within \emph{ACM Computing
Surveys} the nearest are on world models, embodied intelligence, and language-model
navigation, and beyond it a cluster covers vision-language-action models and foundation models
for manipulation---but none organises code-as-policy by degree of self-improvement or names
the \S3.1.5 cell.
\input{tables/tab_survey_compare}
\input{tables/tab_related_surveys}
\FloatBarrier
