\section{A Taxonomy of Robot-Learning Techniques}
\label{sec:taxonomy}

Figure~\ref{fig:taxonomy_main} organises the field into six branches. The dividing
question is \emph{what ships}: frozen weights (\S\ref{sec:vla}) or executable skills
(\S\ref{sec:code}). We tag mechanisms by \textbf{F}eedback, \textbf{S}earch, and
\textbf{M}emory throughout.

Table~\ref{tab:compare_main} compares all systems in the map on what each \emph{ships}, where
it is evaluated, and whether it improves from its own experience.
\input{tables/tab_compare_main}

\subsection{Survey methodology: how the corpus was built}
\label{sec:method}

Figure~\ref{fig:prisma} summarises the corpus construction in the PRISMA~2020
style~\citep{prisma2020}. The corpus was assembled in two passes over a January~2016 to
July~2026 window. First, the 77 taxonomy systems were curated by \emph{seeding and
snowballing}: for each of the six branches we started from its landmark systems and chased
citations forward and backward until new candidates stopped appearing. Second, the 225-work
landscape corpus (Table~\ref{tab:landscape}) was gathered by five \emph{structured web-search
sweeps}, one per area cluster: (i) generalist and vision-language-action policies, imitation
and diffusion policies; (ii) language-model planning, task-and-motion planning, reward and data
synthesis; (iii) skill discovery, hierarchical reinforcement learning, and world models;
(iv) manipulation, dexterity, sim-to-real, locomotion, and benchmarks; and (v) representation
learning, offline reinforcement learning, navigation, and tactile sensing. Each sweep queried
the open web with area-specific search strings of the form ``\emph{<system or family name>
robot learning arXiv}'' and ``\emph{<area> survey/benchmark/dataset}'' over arXiv, the ACM
Digital Library, IEEE Xplore, Google Scholar, and venue proceedings pages (CoRL, RSS, ICRA,
IROS, NeurIPS, ICML, ICLR, CVPR).

\emph{Inclusion} required a work to (a) concern how an embodied agent's skill or policy is
authored, learned, transferred, evaluated, or distributed, and (b) carry verifiable metadata:
exact title, first author, year, and an arXiv identifier or DOI, each confirmed against the
source. \emph{Exclusion} removed pure perception, navigation, and locomotion work with no
bearing on skill authoring (retained only in the landscape appendix where it anchors an area),
works whose metadata could not be verified, and duplicates, detected by both bibliographic key
and arXiv identifier. Every reference in this survey passed the verification step; candidates
that failed it were discarded at harvest time, and we report that their count was not logged
rather than estimate it. Included systems were then mapped onto the taxonomy of
Figure~\ref{fig:taxonomy_main} by the mechanism definitions of Table~\ref{tab:defs}.

\input{figures/fig_prisma}
