\subsection{Benchmarks and Evaluation}
\label{sec:bench}

Progress in the families above is measured on a shared set of simulated benchmarks, most of
which report a single-number success rate. \emph{LIBERO}~\citep{libero} targets lifelong
manipulation and knowledge transfer across task suites; \emph{Meta-World}~\citep{metaworld}
offers fifty manipulation tasks for multi-task and meta-reinforcement learning;
\emph{RLBench}~\citep{rlbench} provides a hundred vision-based tasks with demonstrations; and
\emph{ManiSkill2}~\citep{maniskill2} adds GPU-parallel simulation over twenty task families.
\emph{Robosuite}~\citep{robosuite} is the modular MuJoCo framework underlying many of these,
and \emph{CALVIN}~\citep{calvin} evaluates long-horizon, language-conditioned control by the
average number of sub-tasks completed in a chain. At the high-realism end,
\emph{BEHAVIOR-1K}~\citep{behavior1k} specifies a thousand everyday household activities in a
photorealistic simulator, scoring both success and efficiency.

Table~\ref{tab:matrix} contrasts one exemplar per camp on the axes that separate them. The
recurring gap, and a direct motivation for the open problems of \S\ref{sec:open}, is that
these suites measure \emph{one-shot competence}: they report whether a policy succeeds, not
whether it \emph{improves with experience}. No standard benchmark yet plots held-out success as
a function of accumulated interaction, which is exactly the quantity the self-improvement ladder
of \S\ref{sec:code} is designed to raise.

\input{tables/tab_capability_matrix}

\subsection{Synthesis: what each family cannot do}
\label{sec:synthesis}
Table~\ref{tab:branch_limits} compares every family on six axes: data needs, task horizon,
transfer, interpretability, safety, and characteristic failure mode. Reading it column-wise
profiles a family; reading it row-wise shows that every axis has at least one weak family, and
no family is favourable on all six, which is the tension the skill economy (\S\ref{sec:open})
inherits.

\input{tables/tab_branch_limits}
